% !TeX program = xelatex
% Run with XeLaTeX

\documentclass[]{richard-dang}

\begin{document}
\pagestyle{empty} %to remove the page numbers
 \renewcommand{\labelitemi}{$\diamond$}


\header{Richard}{Dang}
{2B} {Computer Engineering}
{{\faMobile \hspace{\FAspace} +1 (647) 717-0339 
\sep \faEnvelope \hspace{\FAspace}
\href{mailto:r22dang@uwaterloo.ca}{r22dang@uwaterloo.ca}
\sep \faLinkedinSquare \hspace{\FAspace} 
\href{https://linkedin.com/in/dangrichard}{dangrichard} 
\sep \faGithub \hspace{\FAspace}
\href{https://github.com/Richard-Dang}{Richard-Dang}
\sep \faSearch \hspace{\FAspace}
\href{http://richarddang.com}{richarddang.com}
}}

\section*{\faDashboard \hspace{\FAspace} SKILLS}
\begin{tabularcv}
    &  \worktitle{\textbf{LANGUAGES}\hspace{5.6mm}}{Java, JavaScript, HTML, CSS,  Ruby, Python, C/C++}
        \\[\vspacepar] 
    &  \worktitle{\textbf{TECHNOLOGIES}}{Android Studio and Git}
        \\[\vspacepar] 
    &  \worktitle{\textbf{CONCEPTS}\hspace{8mm}}{OOP, REST API, MVC and Agile}
\end{tabularcv}   

\section*{\faGroup \hspace{\FAspace} EXPERIENCES}
\begin{tabularcv}
    May – Sep. 2017   &  
                    \worktitle{Software Developer}{\href{http://hubdoc.com}{Hubdoc}}
                    \begin{tabitemize}
                        \item Designed and implemented a responsive dashboard using \textbf{Express}, \textbf{Backbone} and \textbf{PostgreSQL} that enabled efficient proxy management
                        \item Built and enhanced hundreds of microservices using \textbf{Node} and \textbf{jQuery} that enable bookkeepers to automate compilation of documents, earning over \$200,000 in monthly revenue
                    \end{tabitemize} 
                    \\[\vspacepar] 
    Sep. – Dec. 2016   &   
                    \worktitle{Associate QA Analyst}{\href{http://flipp.com}{Flipp}}
                    \begin{tabitemize}
                        \item Set up continuous integration across multiple projects providing early risk detection, feedback loops, and quick deployments utilizing \textbf{Jenkins}
                        \item Developed automated system checks that allowed for backend health monitoring across all platforms
                        \item Created regression suites with \textbf{Selenium} and test development tools through integration of \textbf{TestRail API}
                        \item Automated performance testing to ensure response times for A/B test framework using \textbf{JMeter}
                    \end{tabitemize} 
                    \\[\vspacepar] 
    Jan. – Apr. 2016   &   
                    \worktitle{Software Test and Tools Developer}{\href{http://geosemi.com}{GEO Semiconductor Inc.}}
                    \begin{tabitemize}
                        \item Validated firmware integrity of over 20 camera sensors/platforms through \textbf{TestLink} and \textbf{JIRA}
                        \item Reduced testing time by over 50\% through automation of testing procedures
                        \item Developed host tools for internal testing/development and designed regression test plans
                    \end{tabitemize} 
\end{tabularcv}   

\section*{\faStar \hspace{\FAspace} PROJECTS}
\begin{tabularcv}
    Jul. 2017 - Present   &   
                    \worktitle{\href{https://github.com/Richard-Dang/AtomLeetCode}{Atom Leetcode}}{Atom Package}
                    \begin{tabitemize}
                        \item Made an \textbf{Atom} package that extracts questions from Leetcode into the text editor with difficulty and language selection 
                    \end{tabitemize} 
                    \\[\vspacepar] 
    Nov. 2016   &   \worktitle{\href{https://github.com/Richard-Dang/AlexaBuddy}{Alexa Buddy}}{Amazon Echo}
                    \begin{tabitemize}
                        \item Created an \textbf{Alexa} app that responds with Reddit posts while filtering out posts containing negative sentiment; won “Best Hack Against Online Harassment” 
                    \end{tabitemize} 
                    \\[\vspacepar]
    May – Jul. 2016   &   
                    \worktitle{\href{https://github.com/Richard-Dang/step-tracker}{Step Tracker}}{Android App}
                    \begin{tabitemize}
                        \item Developed an \textbf{Android} application that utilizes device sensors and finite state machines to track steps and detect direction
                    \end{tabitemize} 
\end{tabularcv}   

\section*{\faMortarBoard \hspace{\FAspace} EDUCATION}
\begin{tabularcv}
    2015 - Present   &   \worktitle{Computer Engineering}{University of Waterloo}
                    \begin{tabitemize}
                        \item Candidate for Bachelor of Applied Science Degree in Computer Engineering
                        \item Received President’s Scholarship for 90-95\% entrance average
                    \end{tabitemize} 
                    \\[\vspacepar] 
\end{tabularcv}

\end{document}