% !TeX program = xelatex
% Run with XeLaTeX

\documentclass[]{richard-dang}

\begin{document}
\pagestyle{empty} %to remove the page numbers
 \renewcommand{\labelitemi}{$\diamond$}


\header{Richard}{Dang}
{3A} {Computer Engineering}
{{\faMobile \hspace{\FAspace} +1 (647) 717-0339 
\sep \faEnvelope \hspace{\FAspace}
\href{mailto:r22dang@uwaterloo.ca}{r22dang@uwaterloo.ca}
\sep \faSearch \hspace{\FAspace}
\href{http://richarddang.com}{richarddang.com}
\sep \faGithub \hspace{\FAspace}
\href{https://github.com/Richard-Dang}{Richard-Dang}
\sep \faLinkedinSquare \hspace{\FAspace} 
\href{https://linkedin.com/in/dangrichard}{dangrichard} 
}}

\section*{\faDashboard \hspace{\FAspace} SKILLS}
\begin{tabularcv}
        &  \worktitle{\textbf{LANGUAGES}\hspace{5.6mm}}{C, C++, CSS, HTML, Java and JavaScript}
            \\[\vspacepar] 
        &  \worktitle{\textbf{TECHNOLOGIES}}{Android Studio, IntelliJ, Git, Spring, Hibernate and SQL Server}
            \\[\vspacepar] 
        &  \worktitle{\textbf{CONCEPTS}\hspace{8mm}}{Agile, Continuous Integration, MVC, OOP, and REST API}
\end{tabularcv}   

\section*{\faGroup \hspace{\FAspace} EXPERIENCE}
\begin{tabularcv}
    Jan – \newline 
    Apr. 2018   &  
                    \href{https://www.ultimatesoftware.com}{
                    \worktitle{Software Engineering}{Ultimate Software}}
                    \begin{tabitemize}
                        \item Introduced numerous functionality to host web app used for managing thousands of Android, Linux, and web time clocks, maintained through \textbf{GWT}, \textbf{Spring and Hibernate}
                        \item Created GDPR Cron job to purge soft-deleted employees by implementing schema constraints to maintain database integrity using \textbf{Liquibase}
                        \item Incorporated features on time clock web app using \textbf{AngularJS} to allow supervisors to override employee check-ins
                    \end{tabitemize} 
                    \\[\vspacepar] 
    May – \newline 
    Sep. 2017   &  
                    \href{http://hubdoc.com}{
                    \worktitle{Software Developer}{Hubdoc}}
                    \begin{tabitemize}
                        \item Implemented an intranet dashboard with \textbf{ExpressJS} and \textbf{BackboneJS} used for proxy management
                        \item Integrated webhook within web app for receiving updated user credential alerts through a \textbf{Slack} app 
                        \item Built and migrated hundreds of document fetching microservices from \textbf{PhantomJS} to \textbf{NightmareJS}, increasing reliability from \textbf{46\%} to \textbf{73\%}
                    \end{tabitemize} 
                    \\[\vspacepar] 
    Sep. – \newline 
    Dec. 2016   &   
                    \href{http://flipp.com}{
                    \worktitle{Associate QA Analyst}{Flipp}}
                    \begin{tabitemize}
                        \item Introduced continuous integration across multiple projects providing early risk detection, feedback loops, and quick deployments utilizing \textbf{Jenkins}
                        \item Developed automated system checks to enable back-end health monitoring across all platforms
                        \item Created front-end regression test suites with \textbf{Selenium} and internal test development tools 
                        \item Automated performance testing to ensure response times for A/B test framework using \textbf{JMeter}
                    \end{tabitemize} 
                    \\[\vspacepar] 
    Jan. – \newline 
    Apr. 2016   &   
                    \href{http://geosemi.com}{
                    \worktitle{Software Test and Tools Developer}{GEO Semiconductor Inc.}}
                    \begin{tabitemize}
                        \item Validated firmware integrity of over \textbf{20} camera sensors/platforms through \textbf{TestLink} and \textbf{JIRA}
                        \item Reduced overall testing time by more than \textbf{50\%} through automation of testing procedures
                        \item Developed host tools for internal testing/development and designed regression test plans
                    \end{tabitemize} 
\end{tabularcv}   

\section*{\faStar \hspace{\FAspace} PROJECTS}
\begin{tabularcv}
    Feb. 2018 - \newline 
    Present   &   
                    \href{https://github.com/Richard-Dang/FindMyResume}{
                    \worktitle{Find My Resume}{Angular 4, Spring Boot and Heroku}}
                    \begin{tabitemize}
                        \item Web app that hosts a collection of uploaded resumes which users can be preview, edit and download
                        \item Demo: \textbf{\href{http://findmyresu.me}{www.findmyresu.me}}
                    \end{tabitemize} 
                    \\[\vspacepar] 
    Jul. -  \newline 
    Aug. 2017   &   
                    \href{https://github.com/Richard-Dang/AtomLeetCode}{
                    \worktitle{Atom Leetcode}{ES6 JavaScript, Node.js, Travis CI and Jasmine}}
                    \begin{tabitemize}
                        \item Atom package that extracts coding challenges and solutions from Leetcode into the Atom text editor
                    \end{tabitemize} 
                    \\[\vspacepar] 
    Nov. 2016   &   \href{https://github.com/Richard-Dang/AlexaBuddy}{
                    \worktitle{Alexa Buddy}{Python, Flask-Ask, Indico API and Reddit API}}
                    \begin{tabitemize}
                        \item Amazon Alexa app that responds with Reddit posts while filtering out negative sentiment
                        \item Won \textbf{\href{https://devpost.com/software/alexabuddy}{Best Hack Against Online Harassment}} at Electric City Hacks
                    \end{tabitemize} 
                    \\[\vspacepar]
    May – \newline 
    Jul. 2016   &   
                    \href{https://github.com/Richard-Dang/step-tracker}{
                    \worktitle{Step Tracker}{Java and Android Studio}}
                    \begin{tabitemize}
                        \item Android app that utilizes device sensors and finite state machines to track steps and detect direction
                    \end{tabitemize} 
\end{tabularcv}   

\section*{\faMortarBoard \hspace{\FAspace} EDUCATION}
\begin{tabularcv}
    2015 - \newline 
    2020   &   \worktitle{Computer Engineering}{University of Waterloo}
                    \begin{tabitemize}
                        \item Candidate for Bachelor of Applied Science Degree in Computer Engineering
                        \item Received President’s Scholarship for \textbf{90-95\%} entrance average
                    \end{tabitemize} 
                    \\[\vspacepar] 
\end{tabularcv}

\end{document}